Resilience and Home-Space for WSTS \thanks{This work was partly done while the author was supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-08-31 final.tex
up

Let us recall the  definition of vector addition system with (control-)states. 
 \begin{definition} 
A {\em vector addition system with states (VASS)} in dimension $d$ ($d$-VASS for short) is a finite $\mathds{Z}^d$-labeled directed graph $V = (Q,T)$, where $Q$ is the set of {\em control-states}, and $T \subseteq Q \times \mathds{Z}^d \times Q$ is the set of {\em control-transitions}. 
 \end{definition} 
%
Subsetquently, $Q \times \N^d$ is the set of states of the transition system associated with a $d$-VASS $V$.
For all states $p(\textbf{u}), q(\textbf{v}) \in Q \times \N^d$ and for every control-transition $t = (p, \textbf{z}, q)$, we write $p(\textbf{u}) \xrightarrow{t} q(\textbf{v})$ whenever $\textbf{v} = \textbf{u} + \textbf{z} \geq \textbf{0}$
%
When in the context of a $d$-VASS, we denote $0^d$ by $\textbf{0}$.

>>>>

Let us recall the  definition of vector addition system with (control-)states. 
 \begin{definition} 
A {\em vector addition system with (control-)states (VASS)} in dimension $d$ ($d$-VASS for short) is a finite $\mathds{Z}^d$-labeled directed graph $V = (Q,T)$, where $Q$ is the set of {\em control-states}, and $T \subseteq Q \times \mathds{Z}^d \times Q$ is the set of {\em control-transitions}. 
 \end{definition} 
%
Subsetquently, $Q \times \N^d$ is the set of states of the transition system associated with a $d$-VASS $V$.
For all states $p(\textbf{u}), q(\textbf{v}) \in Q \times \N^d$ and for every control-transition $t = (p, \textbf{z}, q)$, we write $p(\textbf{u}) \xrightarrow{t} q(\textbf{v})$ whenever $\textbf{v} = \textbf{u} + \textbf{z} \geq \textbf{0}$
%
When in the context of a $d$-VASS, we denote $0^d$ by $\textbf{0}$.
